---
output:
  word_document: default
  html_document: default
  pdf_document: default
---
## Initialize library and load dataset
```{r}
options(scipen = 999)
library(ggplot2)
theme_set(theme_bw())
data("midwest", package = "ggplot2")
```

```{r}
midwest <- read.csv("http://goo.gl/G1K41K")  
```

## Scatter plot
```{r}
gg <- ggplot(midwest, aes(x= area, y= poptotal)) + geom_point(aes(col= state, size = popdensity)) + geom_smooth(method= "loess", se= F) + xlim(c(0,.1)) + ylim(c(0,500000)) + labs(title = "Scatter Plot", subtitle = "Area Vs Population", x = "Area", y = "Population", caption = "Source: midwest")
plot(gg)
```

## Scatterplot with Encircling
```{r}
options(scipen = 999)
library(ggplot2)
library(ggalt)
midwest_select <- midwest[midwest$poptotal > 350000 & 
                            midwest$poptotal <= 500000 & 
                            midwest$area > 0.01 & 
                            midwest$area < 0.1, ]

ggplot(midwest, aes(x= area, y= poptotal)) + geom_point(aes(col= state, size = popdensity)) + geom_smooth(method= "loess", se= F) + xlim(c(0,.1)) + ylim(c(0, 500000)) + geom_encircle(aes(x=area, y=poptotal), data= midwest_select, color= "red", size = 2, expand= 0.08) + labs(title = "Scatter Plot + Encircle", subtitle = "Area Vs Population", x = "Area", y = "Population", caption = "Source:midwest")
```

## Jitter Plot
```{r}
library(ggplot2)
data(mpg, package= "ggplot2")
theme_set(theme_bw())

g <- ggplot(mpg, aes(cty, hwy))

g + geom_point() + geom_smooth(method = "lm", se = F) + labs(title = "Scatterplot with overlapping points", x = "cty", y = "hwy", caption = "Source:midwest")

```

```{r}
library(ggplot2)
data("diamonds", package = "ggplot2")
# View(diamonds)
ggplot(diamonds, aes(x=carat, y=price, color=clarity)) + geom_smooth(se=FALSE)
```
## How to plot correlograms in r?
```{r}
library(ggcorrplot)
data(mtcars) 
corr <- round(cor(mtcars), 1)
ggcorrplot(corr)

```
```{r}
library(maps)
map("state", interior = FALSE)
map("state", boundary = TRUE, col="gray", add = TRUE)
```
## how to make a heatmap in R
```{r}
ds = data.frame(rnorm(5, 50, 20),rnorm(5, 50, 20),rnorm(5, 50, 20),rnorm(5, 50, 20))
rn = c("Arm","Leg","Chest","Gut","Head")
cn = c("Ann","Bob","Tom","Joy")
x = data.matrix(ds, rownames.force = FALSE)
heatmap(x, labRow=rn, labCol=cn, main = "Test Heat Map")
```
## Create a sample of 50 numbers which are incremented by 1.Create the binomial distribution,plot the graph for this sample
```{r}
# Create a sample of 50 numbers which are incremented by 1.
x <- seq(0,50,by = 1)

# Create the binomial distribution.
y <- dbinom(x,50,0.5)

# Plot the graph for this sample.
plot(x,y)

```
## Suppose, a group of 25 people are surveyed as to their beer-drinking preference. The categories were (1) Domestic can, (2) Domestic bottle, (3) Microbrew and (4) import. The raw data is 3 4 1 1 3 4 3 3 1 3 2 1 2 1 2 3 2 3 1 1 1 1 4 3 1 Let’s make Suitable plot of both frequencies and proportions
```{r}
beer = c(3, 4, 1, 1, 3, 4, 3, 3, 1, 3, 2, 1, 2, 1, 2, 3, 2, 3, 1, 1, 1, 1, 4, 3, 1)

barplot(beer)

```

```{r}
barplot(table(beer))
```

```{r}
barplot(table(beer)/length(beer)) 
```

## With the help of mtcar data plot a heat map.
```{r}
# The mtcars dataset:
data <- as.matrix(mtcars, packages = "ggplot2")

# Default Heatmap
heatmap(data)
```

```{r}
data("diamonds")
```


```{r}
ggplot(diamonds, aes(x=carat, y=price, color=clarity)) + geom_smooth(se=FALSE)
```







