## The syntax for constructing ggplots could be puzzling 
 
### The main difference is that, unlike base graphics, ggplot works with dataframes and not individual vectors.
### All the data needed to make the plot is typically be contained within the dataframe supplied to the ggplot() itself or can be supplied to respective geoms. 
### The second noticeable feature is: We keep enhancing the plot by adding more layers (and themes)  to an existing plot created using the ggplot() function.

```{r}
# turn off scientific notation like 1e+06
options(scipen=999)
library(ggplot2)
```

## load the data
```{r}

data("midwest", package = "ggplot2") 

# for alt source # read.csv("http://goo.gl/G1K41K") 
```

## area and poptotal are columns in 'midwest'
```{r}
ggplot(midwest, aes(x=area, y=poptotal))
```
## scatterplot using ggplot
```{r}
ggplot(midwest, aes(x=area, y=poptotal)) + geom_point()
```
## let’s just add a smoothing layer usinggeom_smooth(method='lm'). 
```{r}
g <- ggplot(midwest, aes(x=area, y=poptotal)) + geom_point() + geom_smooth(method = "lm")
plot(g)
```
## To find out what other method options are available for geom_smooth?
```{r}
?geom_smooth
```

## Delete the points outside the limits 
```{r}
g + xlim(c(0, 0.1)) + ylim(c(0, 1000000)) 
```
# Zoom in without deleting the points outside the limits. 
```{r}
# As a result, the line of best fit is the same as the original plot.
g1 <- g + coord_cartesian(xlim=c(0,0.1), ylim=c(0, 1000000))
plot(g1)
```
## To Change the Title and Axis Labels
```{r}
g1 + ggtitle("Area Vs Population", subtitle="From midwest dataset") + xlab("Area") + ylab("Population")

```
## Full Code For the Plot
```{r}
ggplot(midwest, aes(x=area, y=poptotal)) + geom_point() + geom_smooth(method="lm") + coord_cartesian(xlim=c(0,0.1), ylim=c(0, 1000000)) + labs(title="Area Vs Population", subtitle="From midwest dataset", y="Population", x="Area", caption="Midwest Demographics")

```

## To Change the Color and Size of Points
```{r}
g<- ggplot(midwest, aes(x=area, y=poptotal)) + geom_point(col = "steelblue", size = 2) # to change the color and size of scatter points

g1 <- g + geom_smooth(method="lm", col="firebrick", size = 2) # to change the color or smooth line

g1 + coord_cartesian(xlim=c(0,0.1), ylim=c(0, 1000000)) + labs(title="Area Vs Population", subtitle="From midwest dataset", y="Population", x="Area", caption="Midwest Demographics")

```
## To Change the Color To Reflect Categories in Another Column
```{r}
# use aes(col=state) inside geom_point
gg <- ggplot(midwest, aes(x=area, y=poptotal)) + geom_point(aes(col=state), size=3) + geom_smooth(method="lm") + coord_cartesian(xlim=c(0,0.1), ylim=c(0, 1000000)) + labs(title="Area Vs Population", subtitle="From midwest dataset", y="Population", x="Area", caption="Midwest Demographics")

plot(gg)
```
## To hide the legend
```{r}
gg + theme(legend.position="None")
```
## change color palette 
```{r}
gg + scale_color_brewer(palette = "Set1")
```
## To Change the X Axis range
```{r}
gg + scale_x_continuous(breaks=seq(0, 0.1, 0.01)) + scale_y_continuous(breaks = seq(0, 1000000 , 200000))
```
## Change the labels
```{r}
gg + scale_x_continuous(breaks=seq(0, 0.1, 0.01), labels = LETTERS[1:11]) + scale_y_continuous(breaks = seq(0, 1000000 , 200000))
```
## If you need to reverse the scale
```{r}
ggplot(midwest, aes(x=area, y=poptotal)) + geom_point(aes(col=state), size=3) + geom_smooth(method="lm") + coord_cartesian(xlim=c(0.1,0), ylim=c(0, 1000000)) + labs(title="Area Vs Population", subtitle="From midwest dataset", y="Population", x="Area", caption="Midwest Demographics") + scale_x_reverse(lim = c(.1,0))
```
## To Customize the Entire Theme in One Shot using Pre-Built Themes
```{r}
gg + theme_bw() + labs(subtitle="BW Theme") 
```
```{r}
gg + theme_classic() + labs(subtitle="Classic Theme")
```
```{r}
gg <- ggplot(midwest, aes(x= area, y= poptotal)) + geom_point(aes(col=state, size= popdensity)) + geom_smooth(method= "loess", se=F) + coord_cartesian(xlim = c(0,.1), ylim = c(0,500000)) + labs(title= "Area Vs Population", y= "Population", x= "Area", caption = "Source:midwest")

gg + theme(plot.title = element_text(size = 20, face = "bold", family = "American Typewriter", color= "tomato", hjust = 0.5, lineheight = 1.2))
```
## Modifying Legend
```{r}
gg + labs(color = "State", size= "Density")
```
## To Change Legend Labels and Point Colors for Categories
```{r}
gg + scale_color_manual(name= "State", labels= c("Illinois", "Indiana", "Michigan", "Ohio", "Wisconsin"), values = c("IL"="blue", "IN" = "red", "MI"="green", "OH"= "brown", "WI"= "orange"))
```







