## Write a R program to calculate the GCD of two numbers using recursive computation.
```{r}
num1 <- as.integer(readline(prompt = "Enter a number:- "))
num2 <- as.integer(readline(prompt = "Enter another number:- "))

if (num1 < num2){
  smaller <- num1
}else{
  smaller <- num2
}
for (i in 1: smaller){
  if ((num1 %% i == 0) & (num2 %% i == 0)){
    hcf = i
  }
}
print(paste("HCF of number is ", hcf))
```

## Write a function for Make a vector from 1 to 100. Make a for-loop which runs through the whole vector. Multiply the elements which are smaller than 5 and larger than 90 with 10 and the other elements with 0.1., so that you can feed it any vector you like (as argument). Use a for-loop in the function to do the computation with each element.

```{r}
v1 <- c(1:100)
v2 <- c(1:5)
v3 <- c(90:100)
v4 <- c()
for(i in v1){
  if ((i %in% v2)|(i %in% v3)){
    v4 <- append(v4,i*10)
  }else{
    v4 <- append(v4,i*.1)
  }
}
print(v4)
```
## Recursive function to find factorial
```{r}
recursive.factorial <- function(x) {
  if (x == 0){
    return (1)
    }else{
      return (x * recursive.factorial(x-1))
    }
  }
recursive.factorial(5)
```
## Find the sum of natural numbers using the Recursive function.
```{r}
Factorial <- function(N)
{
if (N == 0){
return(1)
}else{
return( N + Factorial (N-1))
}
}
Factorial(9)
```
```{r}
search()
```
```{r}
library()
```













