---
output:
  pdf_document: default
  html_document: default
---
## Find the factorial of a number
```{r}
num <- as.integer(readline(prompt = "Enter a number to find factorial:- "))
fact <- 1
if ((num == 1) & (num == 0)){
  print(paste("Factorial of ", num, " is 0"))
}else{
  for (i in 1:num){
    fact <- fact*i
  }
  print(fact)
}

```
## A number entered by the user is checked whether it's a positive number or a negative number or zero.
```{r}
num <- as.double(readline(prompt = "Enter a number:- "))
if (num > 0){
  print("Its is a positive number")

}else{
  print("Its is a negative number")
}
```
## R Program to Check Prime Number
```{r}
num <- as.integer(readline(prompt = "Enter a number:- "))
count <- 0
for (i in 2:(num-1)){
  if (num%%i == 0){
    count <- count +1
    print(i)
  }
}
if (count == 0){
  print("Its is a prime number")
}else{
  print("Not a prime number")
}
```
## R Program to check Armstrong Number
```{r}
num <- as.integer(readline(prompt = "Enter a number:- "))
temp<- num
sum <- 0
while (temp >0){
  digit = temp %% 10
  sum = sum + (digit ^ 3)
  temp = floor(temp / 10)
}
if (sum == num){
  print("Its is an armstrong number")
}else{
  print("Its is not an armstrong number")
}

```

## Check if a Number is Odd or Even in R Programming
```{r}
num <- as.integer(readline(prompt = "Enter a number:- "))
if (num %% 2 == 0){
  print("It is a even number")
}else{
  print("it is odd number")
}
```
## R program to Find the Factorial of a Number Using Recursion
```{r}
factor <- function(n){
  if (n <= 1){
    return(1)
  }else{
    return( n * factor(n-1))
  }
}
```

```{r}
factor(5)
```
## Use of next function
```{r}
x <- 1:5 
for (val in x) {
	 if (val == 3){ 
	next }
 print(val)
 }
```
## R Program to Find L.C.M.
```{r}
num1 <- as.integer(readline(prompt = "Enter a number:- "))
num2 <- as.integer(readline(prompt = "Enter another number:- "))

if (num1 > num2){
  greater <- num1
}else{
  greater <- num2
}

while (TRUE){
  if ((greater %% num1 == 0) & (greater %% num2 == 0)){
    print(paste("LCM is", greater))
    break
  }else{
    greater <- greater + 1
  }
}
```
## R Program to Find H.C.F.
```{r}
num1 <- as.integer(readline(prompt = "Enter a number:- "))
num2 <- as.integer(readline(prompt = "Enter another number:- "))

if (num1 < num2){
  smaller <- num1
}else{
  smaller <- num2
}
for (i in 1: smaller){
  if ((num1 %% i == 0) & (num2 %% i == 0)){
    hcf = i
  }
}
print(paste("HCF of number is ", hcf))
```

